---
title: "Correlation analysis" 
output: html_notebook
---
This is an Correlation report
Data was taken from MES replication database.
*Wuchtvers_anz* column was extract from MES report system based on DMC using SQL query. </br>
<b>The goal of that report find describe one or more possible scenario in case when:</b>  
 - covariance value; </br> 
 - x depends on y; </br>
 - y depends on x; </br>
 - z depends on x; </br>

```{r}
summary(df)
```
Visualize and checking distribution before normalize dataset
The first one feature is: <b>R_SH</b>
```{r echo=FALSE}
 z_df %>% 
    dplyr::select(-input_DMC, -MD1_ANLIEF_MG, -Wuchtvers_anz, R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```
The next one feature is: <b>Wuchtvers_anz</b>
```{r echo=FALSE}
 z_df %>% 
    dplyr::select(-input_DMC, -MD1_ANLIEF_MG, Wuchtvers_anz, -R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```
The next  one feature is: <b>MD1_ANLIEF_MG</b>                    
```{r echo=FALSE}
 z_df %>% 
    dplyr::select(-input_DMC, -Status, MD1_ANLIEF_MG, -Wuchtvers_anz, -R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```                                                       
The next  one feature is: <b>MD2_ANLIEF_G</b>                    
```{r echo=FALSE}
 z_df %>% 
    dplyr::select(-input_DMC, -Status, -MD1_ANLIEF_MG, -Wuchtvers_anz, -R_SH, MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
``` 
To summarize:</br>
- Skewness > 0 – Right skewed distribution – most values are concentrated on left of the mean, with extreme values to the right.</br>
- Skewness < 0 – Left skewed distribution – most values are concentrated on the right of the mean, with extreme values to the left.</br>
- Skewness = 0 – mean = median, the distribution is symmetrical around the mean. </br>

<p>A small p-value (typically ≤ 0.05) indicates strong evidence against the null hypothesis, so you reject the null hypothesis.

A large p-value (> 0.05) indicates weak evidence against the null hypothesis, so you fail to reject the null hypothesis.

p-values very close to the cutoff (0.05) are considered to be marginal (could go either way). Always report the p-value so your readers can draw their own conclusions.
</p>


  x<-(x - min(x)) / (max(x) - min(x))
Analiza korelacji 
```{r}
ggplot(z_df, aes(x=Wuchtvers_anz, y=R_SH)) + 
     geom_point(color='#2980B9', size = 3) + 
    geom_smooth(method=lm, se=FALSE, fullrange=TRUE, color='#2C3E50')
```





df