---
title: "Correlation analysis"
output: html_notebook
---
This is an Correlation report
Data was taken from MES replication database.
*Wuchtvers_anz* column was extract from MES report system based on DMC using SQL query. </br>
<b>The goal of that report find describe one or more possible scenario in case when:</b>  - covariance value; </br> 
 - x depends on y; </br>
 - y depends on x; </br>
 - z depends on x; </br>

```{r}
summary(df_choose)
```
Visualize and checking distribution before normalize dataset
The first one feature is: <b>R_SH</b>
```{r echo=FALSE}
 z_df_choose %>% 
    dplyr::select(-input_DMC, -MD1_ANLIEF_MG, -Wuchtvers_anz, R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```
The next one feature is: <b>Wuchtvers_anz</b>
```{r echo=FALSE}
 z_df_choose %>% 
    dplyr::select(-input_DMC, -MD1_ANLIEF_MG, Wuchtvers_anz, -R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```
The next  one feature is: <b>MD1_ANLIEF_MG</b>
```{r echo=FALSE}
 z_df_choose %>% 
    dplyr::select(-input_DMC, MD1_ANLIEF_MG, -Wuchtvers_anz, -R_SH, -MD2_ANLIEF_G) %>% 
     gather(Variable, Value) %>% 
     ggplot(aes(x=Value, fill=Variable)) +
     geom_density(alpha=0.4) +
     geom_vline(aes(xintercept=0)) +
    theme_light() +
    scale_fill_brewer(palette="Spectral")
```                                                       